A quantitative framework for investigating the reliability of network construction

### 2018-06-08 manuscript/CI_interactions.tex
Have 30 words to spare now

    Representing an assemblage of species as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. To move from these simpler metrics to a network framework, the tabulation of nodes is combined with interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts significantly with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or may attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species (or pairs of species) can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

      To define the problems associated with quantifying ecological interaction networks, we will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty.

@@

          First, and most fundamentally, we may not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur. In such cases, $\lambda = 0$ and there is no uncertainty.

@@

         Even when an interaction is feasible, i.e. $L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or the lack of suitable habitat. We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology describing the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

@@

        An observed interaction indicates that an interaction was feasible, occurred at the study site during sampling, and was detectable. That is, $L = 1$, $X = 1$, and $D = 1$. An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{concept_fig}). 
        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions? 
        Using empirical data, however, it is impossible to distinguish between sources of variation. An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. This probability does not contain any information about $D$ or $X$. The major question then becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more". Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}) and be able to resolve all interactions with a similar likelihood. For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated and intensive sampling efforts and further reduce uncertainty around unobserved interactions, we suggest researchers use prior information drawn from the same or a similar system. Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for an interaction that has not yet been observed. Say a pair of species has been observed co-occurring $n$ times and observed interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, timing, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]). % The non-point nature of lambda seems like a feature, not a bug.

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution. For species pairs with a great deal of observed data (high $n$), the posterior distribution will mostly be based on the MLE of $\lambda$. Where there is little or no observed data (low $n$), the posterior distribution will reflect our prior knowledge. Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:

@@

      It is common to preform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for this.

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S2} for details and a simple quantitative example).

      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects. The similarity of traits for genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species means that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species.

@@

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network. To do this, we first compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

      It is straightforward to compute most network metrics when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions, and Jensen's inequality states that the average of a non-linear function of a stochastic variable differs from the function of the average of that variable. Any uncertainty in the values of $\lambda$ could therefore bias both the mean and variance of a network metric. One way to avoid potentially biased analytical calculation of network properties is to calculate the properties of a suite of simulated networks.

@@

  Most pairs of species (9,794/12,096 galler-natural enemy pairs) are never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87, variance=28.8; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04, variance=29.3; Fig.~\ref{histograms}B). Moreover, even when a pair of species was observed to interact, the number of interactions was often lower than the number of co-occurrences (Fig.~\ref{histograms}C).

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. This emphasizes the importance of accounting for imperfect detection when analysing empirical networks.

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to treat unobserved interactions as less likely to occur while setting appropriate bounds on interaction probabilities between pairs of species which were never observed co-occurring. The number of observations required to conclude that an interaction is unfeasible is quite high (tens of observations per species pair); some species pairs are likely to fall short of this even in the highest-quality networks. In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions never occur. Moreover, interactions involving species entering new ranges due to climate change or introductions are important for a variety of conservation questions. A Bayesian approach using a trait-matching model or data from species' current ranges could be useful in anticipating how species will integrate into new communities.

@@

  Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (likely the bulk of studies), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

@@

@@

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur. Assume that we want to infer the probability of an interaction between two species, $i$ and $j$, and that this interaction is completely impossible (i.e. the true $\lambda=0$). When estimating $\lambda$, the number of observed interactions will follow a binomial distribution with number of interactions $k$ and number of observations $n$. Using this distribution, we can compute the credible interval of the estimated probability $\lambda$. A single observation of species co-occurrence reveals very little regarding the probability of the interaction as the credible interval for a pair of species with one observation essentially spans from 0 to 1. Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line). Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high. Here we show the upper bound (solid black line) of a 95\% Clopper-Pearson true credible interval for $\lambda$ when $k=0$ ($i$ and $j$ have not been observed interacting) for a variety of $n$. A threshold interaction probability of 0.1 is indicated by the dashed red line. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}

>>>>

    Representing an ecological community as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity on network structure (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to document interactions than species~\citep{Poisot2012}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Poisot2016}. Early work in this vein includes food-web models using likelihood-based approaches~\citep{Allesina2008} or Gaussian~\citep{Williams2010} or binomial~\citep{Rohr2016} probability functions for each possible interaction. These models may include information about species' traits~\citep{Rohr2016} or attempt to reproduce empirical network structures using a set of simple rules~\citep{Allesina2008,Williams2010}.

    Despite these preliminary efforts, we currently lack the quantitative methodology to deal with the uncertainty generated by spatiotemporal variation in ecological interactions and by sampling. Even in extremely well-sampled networks, uneven sampling across species can lead to the erroneous inference that some species do not interact because they co-occur rarely or have not yet been observed together - even if they do interact when they do co-occur (see Fig.~\ref{histograms} for an example). Nearly all network studies will thus neglect some interactions, necessitating an approach that acknowledges this uncertainty.

@@

      We will start from the perspective of an empirical community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. The detection of any interaction is a stochastic process. We define three nested levels of uncertainty contributing to this stochasticity: interaction uncertainty, process uncertainty, and detection uncertainty (Fig.~\ref{concept_fig}).

@@

          First, and most fundamentally, a pair of species may or may not have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur. In such cases, $\lambda = 0$ and there is no uncertainty.

@@

         Even when an interaction is feasible, i.e. $L=1$, it may still not occur at a given location or moment in time because of local constraints such as inclement weather or unsuitable habitat. We define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology describing the contingencies of interactions. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects of other species~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of the factors leading to process uncertainty can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). In the field, however, process uncertainty is likely inevitable.

@@

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable. That is, $L = 1$, $X = 1$, and $D = 1$. An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). 
        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions? 
        Using empirical data, however, it is impossible to identify the cause of an unobserved interaction. An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

@@

        When attempting to reduce uncertainty, the obvious rule of thumb is ``sample more". Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated and intensive sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge to obtain probabilistic networks. We then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Say a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    To properly interpret $\lambda$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution. Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:

@@

      It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

@@

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S2} for details and a simple quantitative example).

      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

@@

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results. One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  Most pairs of species (9,794/12,096 galler-natural enemy pairs) were never found co-occurring and, for species that did occur together, the total number of co-occurrences was generally low (mean=3.87; Fig.~\ref{histograms}A). The bulk of these co-occurring species pairs were never observed to interact: only 7.76\% of galler-natural enemy pairs were observed interacting. Of those pairs that did interact, the incidence of interaction was also low (mean=4.04; Fig.~\ref{histograms}B) and tended to be lower than the number of observed co-occurrences (Fig.~\ref{histograms}C).

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, less than 10\% of species pairs were observed interacting, and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. As such, increasing sampling is likely to add more zeros than ones to an interaction network.

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring. In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions cannot occur. This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  Based on the framework described above, we offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

@@

  \begin{figure}[h!]
    \caption{Three nested levels of uncertainty mean that the zeros (unobserved interactions) and ones (observed interactions) in an interaction matrix are not equally certain. A one indicates an interaction that definitely occurred, while a zero could indicate an interaction that never occurs, an interaction that occurs sometimes but did not occur during sampling, or an interaction that occurred but was not detected. If the large rectangle represents the probability space for an interaction, only the shaded areas represent accurate records of the interaction probability.}
    \label{conceptual_fig}
    \begin{center}
    \end{center}
    \end{figure}

@@

  \begin{figure}[h!]
    \caption{Imperfect detection of interactions increases the number of samples required to be confident that an interaction does not occur. Assume that two species cannot interact (i.e., $\lambda=0$) and that the number of observed interactions follows a binomial distribution. Here we show the upper bound (solid black line) of a 95\% Cloper-Pearson true credible interval for the interaction probability $\lambda$ for a pair of species that has been observed co-occurring $n$ times but never observed interacting ($k = 0$). Only with 35 observations will the upper limit of the credible interval be lowered to 0.1 (dashed, red line). Thus, adding more observations is useful in controlling uncertainty, but the number of observations added needs to be very high. }
    \label{upper_limits}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/upper_limit_DG.eps}
    \end{center}
    \end{figure}
